---
title: "Task_12"
author: watsoncl 
output: 
  html_document:
    keep_md: true
    theme: flatly
    toc: true
    toc_float: true
    code_folding: hide
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(readxl)
library(readr)
library(dplyr)
library(ggplot2)
library(devtools)
library(RCurl)
library(blscrapeR)
library(stringr)
```

##Background
Using global regular expression print (grep) and regular expressions (regex) to find character string patterns is a valuable tool in data analysis and is available with all operating systems and many different programming languages. It is a powerful tool once it is understood. The recently developed library(stringr) package makes these tools much easier to use. The three tasks below can be completed in many different ways. As a challenge, my code to complete this entire task less than 10 lines.

##Reading

This reading will help you complete the tasks below.

o [Chapter 14: R for Data Science - Strings](r4ds.had.co.nz/strings.html)

o [Five principles of effective data visualizations](https://www.thoughtworks.com/insights/blog/five-principles-effective-data-visualizations)

o [regexr.com (optional)](https://regexr.com/)

o [Regular Expression examples (optional)](https://qntm.org/files/re/re.html)

o [Regular Expression support applet (optional)](https://regex101.com/)

o [Regular Expression for R (optional)](http://stat545.com/block022_regular-expression.html)

##Tasks

[x] Use the readr::read_lines() function to read in each string - randomletters.txt and randomletters_wnumbers.txt

```{r, include=FALSE}
library(stringr)
library(pander)
rletter <- readr::read_lines("https://byuistats.github.io/M335/data/randomletters.txt")
rnumber <- readr::read_lines("https://byuistats.github.io/M335/data/randomletters_wnumbers.txt")

```

[x] With the randomletters.txt file, pull out every 1700 letter (e.g. 1, 1700, 3400, …) and find the quote that is hidden - the quote ends with a period

````{r, include=FALSE}
##Code from Class
##Pull out every 1700 letter (e.g. 1, 1700, 3400, ) 

Letters <- str_split(rletter, "")[[1]][c(1, seq(1700, str_count(rletter), by = 1700))] 

pander(Letters)

## find all the numbers hidden and convert those numbers to letters using the letters order in the alphabet to decipher the message

```

[x] With the randomletters_wnumbers.txt file, find all the numbers hidden and convert those numbers to letters using the letters order in the alphabet to decipher the message

```{r}
pander(Letters)
```

[x] With the randomletters.txt file, remove all the spaces and periods from the string then find the longest sequence of vowels.

```{r, include=FALSE}
## with numbers 

extr_numbers <- rnumber %>%
  str_extract_all("[0-9]+") %>%
  unlist() %>%
  parse_number()

## letters is a default object in R

letters[extr_numbers]

## longest sequence of vowels without blank spaces and periods

Number <- rnumber %>%
  str_replace(" ", "") %>%
  str_replace("\\.", "") %>%
  str_extract_all("[aeiou]{7}")

## str_count("[aeiou]{7}")
```

```{r}
pander(Number)
```

[x] Save your .R script to your repository and be ready to share your code solution at the beginning of class

















